Gaia's constraints on the extremely massive ($\sim$$150\,M_\odot$) runaway star candidate VFTS682

### 2018-06-10 VFTS682_APJL.tex
added angle, stopping now

    %  &RA &[degree] &  \phantom{-}84.73 % $\pm$  0.03
   %                     & \multirow{2}{*}{\cite{evans:11}}\\[5pt]
    %  &DEC & [degree] & -69.07 % $\pm$  0.05
     %                   & \\[5pt]
      \multicolumn{5}{l}{\emph{Gaia's relative proper motion for VFTS
      682 }} \\
      \hline
      &$\delta\mu_\mathrm{RA}$  &[$\masyr$] & 0.103$\pm$0.080 & (1,4) \\
      &$\delta\mu_\mathrm{DEC}$  &[$\masyr$] & 0.086$\pm$0.100 &  (1,4) \\
      &$\delta\mu_\mathrm{}$  &[$\masyr$] & \SdM{0.13}$\pm$\SdM{0.09} &  (1,4) \\
                 &$v_\mathrm{2d}$  &[$\kms$] & \SdM{32}$\pm$\SdM{21} & (1,4)\\  
                     &$\theta^{*}$  &[degrees] &  \SdM{xxx}$\pm$\SdM{xxx}  & (1,4)\\  
                         &$v_\mathrm{2d, \parallel}$  &[$\kms$] & \SdM{xxx}$\pm$\SdM{xxx} & (1,4)\\  
 %

@@

VFTS682 is identified with the source id 4657685637907503744 in the
\emph{Gaia} DR2 catalog  as a 15.65 mag star in the G band
\citep{gaia:16,brown:18}.   The number of visibility periods,
i.e. groups of observations separated from other groups by a gap of at
least 4 days, used in the astrometric solution is 17 for this
star. The reported astrometric excess noise is zero.  These values
suggest that the \emph{Gaia} DR2  data for VFTS682 are
reliable. Generally the Gaia errors are correlated  \citep[][]{lindengren:18}, but the correlation coefficients are small for this star% , see Tab.~\ref{tab:vfts682}
. We can therefore treat the proper motion components as uncorrelated.

>>>>

    %  &RA &[degree] &  \phantom{-}84.73 % $\pm$  0.03
   %                     & \multirow{2}{*}{\cite{evans:11}}\\[5pt]
    %  &DEC & [degree] & -69.07 % $\pm$  0.05
     %                   & \\[5pt]
      \multicolumn{5}{l}{\emph{Gaia's relative proper motion for VFTS
      682 }} \\
      \hline
      &$\delta\mu_\mathrm{RA}$  &[$\masyr$] & 0.103$\pm$0.080 & (1,4) \\
      &$\delta\mu_\mathrm{DEC}$  &[$\masyr$] & 0.086$\pm$0.100 &  (1,4) \\
      &$\delta\mu_\mathrm{}$  &[$\masyr$] & \SdM{0.13}$\pm$\SdM{0.09} &  (1,4) \\
                 &$v_\mathrm{2d}$  &[$\kms$] & \SdM{32}$\pm$\SdM{21} & (1,4)\\  
                     &$\theta$  &[degrees] &  14.2$\pm$\SdM{xxx}  & (1,4)\\  
                         &$v_\mathrm{2d, \parallel}$  &[$\kms$] & \SdM{xxx}$\pm$\SdM{xxx} & (1,4)\\  
 %

@@

VFTS682 is identified with the source id 4657685637907503744 in the
\emph{Gaia} DR2 catalog  as a 15.65 mag star in the G band
\citep{gaia:16,brown:18}.   The number of visibility periods,
i.e. groups of observations separated from other groups by a gap of at
least 4 days, used in the astrometric solution is 17 for this
star. The reported astrometric excess noise is zero.  These values
suggest that the \emph{Gaia} DR2  data for VFTS682 are
reliable. Generally, the Gaia errors are correlated
\citep[][]{lindengren:18}, but for this star the correlation coefficient is small, see Tab.~\ref{tab:vfts682}
. We can therefore treat the proper motion components as uncorrelated.
